---
title: "Md. Jubayer Hossain"
output:
  html_document:
    css: css/website-cv.css
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(knitr)
library(glue)
library(fontawesome)
library(DT)
library(lubridate)
library(readxl)
source("R/utility-functions.R")

cv_entries <- read_excel("CV_Data_HossainMJ.xlsx", sheet = "cv_entries") |> 
  mutate(year = year(date))
publications <- read_excel("CV_Data_HossainMJ.xlsx", sheet = "publications") |> 
  mutate(year = year(date))
```

[`r fa("envelope")`](hossainmj.me@gmail.com)
[`r fa("github")`](https://github.com/hossainlab)
[`r fa("orcid")`](https://orcid.org/0000-0001-9323-4997)
[`r fa("researchgate")`](https://www.researchgate.net/profile/Md-Jubayer-Hossain-2)
[`r fa("linkedin")`](https://www.linkedin.com/in/hossainmj/)


## Summary

I am *[Md. Jubayer Hossain](https://hossainlab.github.io/)*. I am the founder and Executive Director of [CHIRAL Bangladesh](https://chiralbd.org/), a non-profit biomedical research organization dedicated to solving public health problems in Bangladesh. Additionally, I am also working as a health data analysis instructor at [cBLAST](https://www.cblastdu.xyz/). My professional endeavors aim to maximize the quality of life for individuals by operating at the intersection of education, technology, and health research.


[`r fa("download")` CV as PDF]()

## Research Interest
Focusing on cancer epidemiology, my research experience encompasses designing and implementing projects to address public health challenges. By leveraging big data in healthcare and conducting population-based studies, my approach aimed to uncover trends, risk factors, and outcomes related to cancer. By utilizing diverse methodologies, I strive to inform preventive strategies and treatment approaches, ultimately contributing to the advancement of cancer prevention.

## Education and Training 

```{r}
education <- read_excel("CV_Data_HossainMJ.xlsx", sheet = "education") 
education  |> 
  mutate(
    degree = paste(
      "<span class='cv-entry-title'>", 
      degree,"</span>,", 
      institution, "</span>,",
      where, 
      "<br>", 
      details
    )
  )  |> 
  select(year, degree)  |> 
  kable(escape = FALSE)
```


## Research Experiences {.domain-header}

```{r}
research <- read_excel("CV_Data_HossainMJ.xlsx", sheet = "research") 

research |>  
  mutate(role = str_c("<span class='cv-entry-title'>",
                      role, "</span><br>", 
                      institution, 
                      "<br>", 
                      details)) |> 
  select(dates, role) |> 
  kable(escape = FALSE)
```


## Teaching Experience

```{r, teaching-experience}
teaching <- read_excel("CV_Data_HossainMJ.xlsx", sheet = "teaching") 
teaching |> 
  mutate(role = ifelse(!is.na(details), 
    str_c("<span class='cv-entry-title'>", role, "</span><br class='work-break'>", institution, "<br>", details),
    str_c("<span class='cv-entry-title'>", role, "</span><br class='work-break'>", where))) |> 
  select(dates, role) |> 
  kable(escape = FALSE)
  
```

## Courses and Workshops

```{r, courses-workshops}
courses <- read_excel("CV_Data_HossainMJ.xlsx", sheet = "courses") 
courses |> 
  mutate(role = ifelse(!is.na(details), 
    str_c("<span class='cv-entry-title'>", role, "</span>,",  title,  "</span><br class='work-break'>", institution, "<br>", details),
    str_c("<span class='cv-entry-title'>", role, "</span><br class='work-break'>", institution))) |> 
  select(dates, role) |> 
  kable(escape = FALSE)
```

## Skills
```{r, skills}
skills <- read_excel("CV_Data_HossainMJ.xlsx", sheet = "skills") 

skills |> 
  mutate(icon = case_when(
    str_detect(what, "Programming") ~ "code",
    str_detect(what, "Data Science") ~ "code",
    str_detect(what, "GIS & Remote Sensing") ~ "code",
    str_detect(what, "Survey Tools") ~ "code",
    str_detect(what, "Analytics Softwares") ~ "code",
    str_detect(what, "Bioinformaticss") ~ "code",
    str_detect(what, "Academic Writing Tools") ~ "code",
    str_detect(what, "Reproducible Research") ~ "flask",
    str_detect(what, "Web") ~ "laptop",
    str_detect(what, "Miscellaneous Skills") ~ "laptop"
  )) |> 
  rowwise() |> 
  mutate(what = str_c(fa(icon), "&nbsp;<span class='cv-entry-title'>", what, "</span> ", additional_info)) |> 
  select(what) |> 
  kable(escape=FALSE)
```
